<<<<<<< HEAD:Ada_Idaho.Rmd
---
title: "Cointegration_2(general)"
author: "Syed Mohammed Tareq"
date: "4/1/2021"
output: html_document
---

```{r}


library(urca)
library(forecast)
library(tidyverse)
#install.packages("vars")
library(vars)
library(lmtest)

```




```{r}

# Loading the Dataset

data_frame = read_csv("https://raw.githubusercontent.com/QinLab/COVID19_transmission_MS/main/county3RWM/Ada%2C%20Idaho%2C%20US.csv?token=APMEIZGLIXD6ZKG7YGAJQCLANZSNC")

# data_frame <- read_csv("Data_Covid.csv")
data_frame[is.na(data_frame)] = 0
data_frame



```
```{r}

# DailyCases were converted into time series data. Since dates were not mentioned in the  Date format (shown as string)
# Thus general index were used (1 to 248)
# Declaring time series object
dailyCases_ts = ts(data_frame$dailyCases, start = 1, end=248, frequency = 1)
air_temp_ts = ts(data_frame$air_temp, start = 1, end=248, frequency = 1)
RH_ts = ts(data_frame$RH, start = 1, end=248, frequency = 1)
Rt_ts = ts(data_frame$Rt, start = 1, end=248, frequency = 1)
apple_driving_ts = ts(data_frame$AppleDriving, start = 1, end=248, frequency = 1)
Google_workplace_ts = ts(data_frame$GoogleWorkplace, start = 1, end=248, frequency = 1)
Google_residential_ts = ts(data_frame$GoogleResidential, start = 1, end=248, frequency = 1)



```


Lag values 


2 ~ 10    range of total lag Value
7 ~ 10    range of lag value  K=  1/4 OF DATE 




# Bind into a system


compare : 

Rt_ts : Reproduction No
air_temp_ts : air temperature 


```{r}
system1 = cbind(Rt_ts, air_temp_ts)
head(system1)

```


compare : 

Rt_ts : Reproduction No
air_temp_ts : Air temperature 

```{r}

system2 = cbind(Rt_ts, RH_ts)
head(system2)

```

compare : 

Rt_ts : Reproduction No
RH_ts : Relative humadity 
                
```{r}               
                
system3 = cbind(Rt_ts, apple_driving_ts)
head(system3)

```



```{r}
system4 = cbind(Rt_ts, Google_workplace_ts)
head(system4)

```

```{r}

system5 = cbind(Rt_ts, Google_residential_ts)
head(system5)

```

```{r}
# lag selection using VAR technique
lagselect1 = VARselect(system1, lag.max = 7, type = "const")
lagselect1


#lagselect1$selection

lagselect1$selection #   
as.factor(lagselect1$selection)
summary(as.factor(lagselect1$selection))
sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])

K_val1 =strtoi(names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]))-1
K_val1



# suggestion value
if (K_val1<2){
  K_val1=2
  
}


```

AIC : 
# results for system2








```{r}

# lag = 7

# time-point 100 days    before 100 days  then forecast  next 100 day data 

lagselect2 = VARselect(system2, lag.max = 7, type = "const")
#lagselect2$selection
K_val2 =strtoi(names(sort(summary(as.factor(lagselect2$selection)), decreasing=T)[1]))-1

if (K_val2<2){
  K_val2=2
}
K_val2
```


# results for system3

```{r}


lagselect3 = VARselect(system3, lag.max = 7, type = "const")
#lagselect3$selection
K_val3 =strtoi(names(sort(summary(as.factor(lagselect3$selection)), decreasing=T)[1]))-1

if (K_val3<2){
  K_val3=2
}

K_val3

```
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
$criteria
              1        2        3        4        5        6        7
AIC(n) 1.128403 1.095402 1.104286 1.110670 1.139414 1.177879 1.172366
HQ(n)  1.198310 1.217739 1.279053 1.337866 1.419041 1.509936 1.556853
SC(n)  1.301920 1.399057 1.538079 1.674599 1.833481 2.002085 2.126709
FPE(n) 3.090744 2.990532 3.017503 3.037346 3.126771 3.250677 3.234567

> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 

> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     7      7      1      7      
Levels: 1 7
> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2
> sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
1 
2 
> names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])
[1] "1"


    
```{r}

lagselect4 = VARselect(system4, lag.max = 7, type = "const")
#lagselect3$selection
K_val4 =strtoi(names(sort(summary(as.factor(lagselect4$selection)), decreasing=T)[1]))-1

if (K_val4<2){
  K_val4=2
}

K_val4

```


```{r}

lagselect5 = VARselect(system5, lag.max = 7, type = "const")
#lagselect3$selection
K_val5 =strtoi(names(sort(summary(as.factor(lagselect5$selection)), decreasing=T)[1]))-1

if (K_val5<2){
  K_val5=2
}

K_val5

```


```{r}


# Johansen testing(trace)


# Test 1

test1 = ca.jo(system1, type='trace', ecdet = 'const', K=K_val1)
print(summary(test1))

# Test 2

test2 = ca.jo(system2, type='trace', ecdet = 'const', K=K_val2)
summary(test2)

# Test 3

test3 = ca.jo(system3, type='trace', ecdet = 'const', K=K_val3)
summary(test3)

# Test 4

test4 = ca.jo(system4, type='trace', ecdet = 'const', K=K_val4)
summary(test4)

# Test 5 

test5 = ca.jo(system5, type='trace', ecdet = 'const', K=K_val5)
summary(test5)


```

>summary(test1)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.805645e-01 7.491011e-02 1.917411e-02 5.531697e-18

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.76  7.52  9.24 12.97
r <= 1 | 23.92 17.85 19.96 24.60
r = 0  | 72.91 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                 dailyCases_ts.l2   Rt_ts.l2 air_temp_ts.l2    constant
dailyCases_ts.l2         1.000000    1.00000       1.000000    1.000000
Rt_ts.l2                 9.211152  -49.94739    -356.541761  828.080675
air_temp_ts.l2          -3.110456   13.14016       4.914035   -3.021227
constant                49.012173 -274.78631     282.399152 -164.033669

Weights W:
(This is the loading matrix)

                dailyCases_ts.l2      Rt_ts.l2 air_temp_ts.l2      constant
dailyCases_ts.d    -0.3925821122 -3.068507e-02  -4.581181e-03 -5.476077e-18
Rt_ts.d            -0.0002729301 -4.053662e-05   3.553009e-05 -3.788555e-21
air_temp_ts.d       0.0267354806 -7.791316e-03  -4.606410e-04  3.230168e-19

> summary(test2)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 2.649299e-01 1.139255e-01 6.869784e-02 1.110223e-16

Values of teststatistic and critical values of test:

           test 10pct  5pct  1pct
r <= 2 |  17.51  7.52  9.24 12.97
r <= 1 |  47.26 17.85 19.96 24.60
r = 0  | 122.98 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                    dailyCases_ts.l2     RH_ts.l2 apple_driving_ts.l2    constant
dailyCases_ts.l2           1.0000000   1.00000000            1.000000    1.000000
RH_ts.l2                  -8.9556211   0.18907898            6.123974    2.939054
apple_driving_ts.l2        0.3847621  -0.09244073            3.778865    1.394470
constant                 621.6903883 -12.39140162        -1103.827748 2208.110923

Weights W:
(This is the loading matrix)

                   dailyCases_ts.l2    RH_ts.l2 apple_driving_ts.l2      constant
dailyCases_ts.d         -0.03040052 -0.30292247        -0.006422801 -1.593734e-18
RH_ts.d                  0.05456596 -0.01887693        -0.002105843  3.767369e-19
apple_driving_ts.d      -0.09475738  0.24351208        -0.039664552 -1.121429e-17

> summary(test3)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 9.792497e-02 4.007579e-02 2.756594e-02 4.163336e-17

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  6.76  7.52  9.24 12.97
r <= 1 | 16.66 17.85 19.96 24.60
r = 0  | 41.60 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                         dailyCases_ts.l6 Google_workplace_ts.l6 Google_residential_ts.l6    constant
dailyCases_ts.l6                   1.0000               1.000000                 1.000000   1.0000000
Google_workplace_ts.l6          -118.3593               1.463141                -0.188060  -2.3164169
Google_residential_ts.l6        -317.5302              -5.856418                 1.804158  -0.6564643
constant                       -1110.0112              43.927921               -25.694469 313.4928351

Weights W:
(This is the loading matrix)

                        dailyCases_ts.l6 Google_workplace_ts.l6 Google_residential_ts.l6      constant
dailyCases_ts.d            -0.0001196841            -0.05311015              -0.12600019  1.187801e-18
Google_workplace_ts.d       0.0023961852            -0.03057509               0.01638121  6.280028e-19
Google_residential_ts.d     0.0003040770             0.0225


# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (34.91) < test value (72.91). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature.In the second hypothesis (r=1),value of 5 pct (19.96) < test value(23.92). Therefore there exist more than 2 co-integration relationship. Since in 3rd hypothesis, test value(4.76)< 5pct, existence of more than 3 co-integration relationship invalidated. Thus at most there are 2 co-integration relationship existed.
# Since in 3rd hypothesis, test value (17.51) > 5pct (9.24), there are more than 3 co-integration relationship existed between daily cases, Rh and apple driving.
# Since in 2nd hypothesis, test value (16.66) < 5pct (19.96), there are at most 1 co-integration relationship existed.




```{r}

# Johansen testing(MaxEigen)

print("------Eigen value testing----")

test1ei = ca.jo(system1, type='eigen', ecdet = 'const', K=K_val1)
test2ei = ca.jo(system2, type='eigen', ecdet = 'const', K=K_val2)
test3ei = ca.jo(system3, type='eigen', ecdet = 'const', K=K_val3)
test4ei = ca.jo(system4, type='eigen', ecdet = 'const', K=K_val4)
test5ei = ca.jo(system5, type='eigen', ecdet = 'const', K=K_val5)

summary(test1ei)
summary(test2ei)
summary(test3ei)
summary(test4ei)
summary(test5ei)

```

> summary(test1ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.805645e-01 7.491011e-02 1.917411e-02 5.531697e-18

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.76  7.52  9.24 12.97
r <= 1 | 19.15 13.75 15.67 20.20
r = 0  | 48.99 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                 dailyCases_ts.l2   Rt_ts.l2 air_temp_ts.l2    constant
dailyCases_ts.l2         1.000000    1.00000       1.000000    1.000000
Rt_ts.l2                 9.211152  -49.94739    -356.541761  828.080675
air_temp_ts.l2          -3.110456   13.14016       4.914035   -3.021227
constant                49.012173 -274.78631     282.399152 -164.033669

Weights W:
(This is the loading matrix)

                dailyCases_ts.l2      Rt_ts.l2 air_temp_ts.l2      constant
dailyCases_ts.d    -0.3925821122 -3.068507e-02  -4.581181e-03 -5.476077e-18
Rt_ts.d            -0.0002729301 -4.053662e-05   3.553009e-05 -3.788555e-21
air_temp_ts.d       0.0267354806 -7.791316e-03  -4.606410e-04  3.230168e-19

> summary(test2ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.477626e-01 2.708232e-02 1.822228e-02 2.316317e-19

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.45  7.52  9.24 12.97
r <= 1 |  6.64 13.75 15.67 20.20
r = 0  | 38.69 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                    dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6    constant
dailyCases_ts.l6           1.0000000   1.0000000            1.000000   1.0000000
RH_ts.l6                  -7.3608407   0.3965370            4.360072   0.4842979
apple_driving_ts.l6        0.2902885  -0.1255131            2.626363   1.0932876
constant                 511.1520401 -23.4892054         -793.423732 193.5741575

Weights W:
(This is the loading matrix)

                   dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6      constant
dailyCases_ts.d         -0.04837831 -0.14244464       -0.0052139939 -8.734074e-18
RH_ts.d                  0.06890610 -0.01469317       -0.0009433436  1.060041e-17
apple_driving_ts.d      -0.07231963  0.13641215       -0.0292459512 -1.060074e-17

> summary(test3ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 2.563121e-01 1.656282e-01 1.064700e-01 5.551115e-17

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 | 27.69  7.52  9.24 12.97
r <= 1 | 44.54 13.75 15.67 20.20
r = 0  | 72.85 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                         dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2    constant
dailyCases_ts.l2                1.0000000               1.000000                1.0000000    1.000000
Google_workplace_ts.l2         -0.4256884               3.446944               -0.5514188   -2.421722
Google_residential_ts.l2      -32.5242728               2.638470               -0.6803409   -1.856409
constant                      120.7067169              46.826178              -21.0843814 2177.286869

Weights W:
(This is the loading matrix)

                        dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2      constant
dailyCases_ts.d              0.011721881           -0.067451919              -0.26677034 -6.030348e-19
Google_workplace_ts.d       -0.008666682           -0.101053527               0.06610875  1.371053e-18
Google_residential_ts.d      0.018170612            0.005979858              -0.00418403 -4.553892e-20

> 

# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (22.00) < test value (48.99). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature. In the second hypothesis (r=1),value of 5 pct (15.67) < test value(19.15). Therefore there exist more that 2 co-integration relationship. Since in 3rd hypothesis, test value (4.76) < 5pct(9.24), existence of more than 3 co-integration relationship invalidated. Thus there exist at most 2 co-integration relationship.
# Only 1 co-integration relationship exist between daily cases, Rh and apple driving.
# There are more than 3 co-integration relationship exist between daily cases, goggle workplace and goggle residential.





=======
---
title: "Cointegration_2"
author: "Syed Mohammed Tareq"
date: "2/26/2021"
output: html_document
---


```{r}


library(urca)
library(forecast)
library(tidyverse)
#install.packages("vars")
library(vars)
library(lmtest)

```




```{r}

# Loading the Dataset

#data_frame = read_csv("https://raw.githubusercontent.com/QinLab/COVID19_transmission_MS/main/county3RWM/Acadia%2C%20Louisiana%2C%20US.csv?token=APMEIZDYFM5QZG4AMN5DE4K72HT6O")

data_frame <- read_csv("Data_Covid.csv")
data_frame[is.na(data_frame)] = 0
data_frame



```
```{r}

# DailyCases were converted into time series data. Since dates were not mentioned in the  Date format (shown as string)
# Thus general index were used (1 to 248)
# Declaring time series object
dailyCases_ts = ts(data_frame$dailyCases, start = 1, end=248, frequency = 1)
air_temp_ts = ts(data_frame$air_temp, start = 1, end=248, frequency = 1)
RH_ts = ts(data_frame$RH, start = 1, end=248, frequency = 1)
Rt_ts = ts(data_frame$Rt, start = 1, end=248, frequency = 1)
apple_driving_ts = ts(data_frame$AppleDriving, start = 1, end=248, frequency = 1)
Google_workplace_ts = ts(data_frame$GoogleWorkplace, start = 1, end=248, frequency = 1)
Google_residential_ts = ts(data_frame$GoogleResidential, start = 1, end=248, frequency = 1)



```


Lag values 


2 ~ 10    range of total lag Value
7 ~ 10    range of lag value  K=  1/4 OF DATE 




# Bind into a system


compare : 

Rt_ts : Reproduction No
air_temp_ts : air temperature 


```{r}
system1 = cbind(Rt_ts, air_temp_ts)
head(system1)

```


compare : 

Rt_ts : Reproduction No
air_temp_ts : Air temperature 

```{r}

system2 = cbind(Rt_ts, RH_ts)
head(system2)

```

compare : 

Rt_ts : Reproduction No
RH_ts : Relative humadity 
                
```{r}               
                
system3 = cbind(Rt_ts, apple_driving_ts)
head(system3)

```



```{r}
system4 = cbind(Rt_ts, Google_workplace_ts)
head(system4)

```

```{r}

system5 = cbind(Rt_ts, Google_residential_ts)
head(system5)

```

```{r}
# lag selection using VAR technique
lagselect1 = VARselect(system1, lag.max = 7, type = "const")
lagselect1


#lagselect1$selection

lagselect1$selection #   
as.factor(lagselect1$selection)
summary(as.factor(lagselect1$selection))
sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])

K_val1 =strtoi(names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]))-1
K_val1



# According to Johansen criteria
if (K_val1<2){
  K_val1=2
  
}


```

AIC : 
# results for system2








```{r}

# lag = 7

# time-point 100 days    before 100 days  then forecast  next 100 day data 

lagselect2 = VARselect(system2, lag.max = 7, type = "const")
#lagselect2$selection
K_val2 =strtoi(names(sort(summary(as.factor(lagselect2$selection)), decreasing=T)[1]))-1

if (K_val2<2){
  K_val2=2
}
K_val2
```


# results for system3

```{r}


lagselect3 = VARselect(system3, lag.max = 7, type = "const")
#lagselect3$selection
K_val3 =strtoi(names(sort(summary(as.factor(lagselect3$selection)), decreasing=T)[1]))-1

if (K_val3<2){
  K_val3=2
}

K_val3

```
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
$criteria
              1        2        3        4        5        6        7
AIC(n) 1.128403 1.095402 1.104286 1.110670 1.139414 1.177879 1.172366
HQ(n)  1.198310 1.217739 1.279053 1.337866 1.419041 1.509936 1.556853
SC(n)  1.301920 1.399057 1.538079 1.674599 1.833481 2.002085 2.126709
FPE(n) 3.090744 2.990532 3.017503 3.037346 3.126771 3.250677 3.234567

> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 

> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     7      7      1      7      
Levels: 1 7
> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2
> sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
1 
2 
> names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])
[1] "1"


    
```{r}

lagselect4 = VARselect(system4, lag.max = 7, type = "const")
#lagselect3$selection
K_val4 =strtoi(names(sort(summary(as.factor(lagselect4$selection)), decreasing=T)[1]))-1

if (K_val4<2){
  K_val4=2
}

K_val4

```


```{r}

lagselect5 = VARselect(system5, lag.max = 7, type = "const")
#lagselect3$selection
K_val5 =strtoi(names(sort(summary(as.factor(lagselect5$selection)), decreasing=T)[1]))-1

if (K_val5<2){
  K_val5=2
}

K_val5

```


```{r}


# Johansen testing(trace)


# Test 1

test1 = ca.jo(system1, type='trace', ecdet = 'const', K=K_val1)
print(summary(test1))


```
```{r}
# Cointegration equation 

w = Rt_ts - 0.2585501*air_temp_ts + 5.0689288

xMat <- t(data.matrix(cbind(system1[c(6:3)],ones)))
beta <- data.matrix(test1@V[,1])
wt <- t(beta) %*% (xMat) 
# wt = Y$Rs_ts - (0.2585501)*Y$air_temp_ts + 5.0689288
plot(t(wt), type="l", main="Stationary Spread Series",
     xlab="Time", ylab="Spread")
wtAdf <- ur.df(t(wt))
wtAdf@cval
#      1pct  5pct 10pct
# tau1 -2.58 -1.95 -1.62
wtAdf@teststat # fail to reject null of unit-root
#                tau1
# statistic -4.037032

```
```{r}
# Test 2

test2 = ca.jo(system2, type='trace', ecdet = 'const', K=K_val2)
summary(test2)

# Test 3

test3 = ca.jo(system3, type='trace', ecdet = 'const', K=K_val3)
summary(test3)

# Test 4

test4 = ca.jo(system4, type='trace', ecdet = 'const', K=K_val4)
summary(test4)

# Test 5 

test5 = ca.jo(system5, type='trace', ecdet = 'const', K=K_val5)
summary(test5)


```

>summary(test1)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.805645e-01 7.491011e-02 1.917411e-02 5.531697e-18

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.76  7.52  9.24 12.97
r <= 1 | 23.92 17.85 19.96 24.60
r = 0  | 72.91 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                 dailyCases_ts.l2   Rt_ts.l2 air_temp_ts.l2    constant
dailyCases_ts.l2         1.000000    1.00000       1.000000    1.000000
Rt_ts.l2                 9.211152  -49.94739    -356.541761  828.080675
air_temp_ts.l2          -3.110456   13.14016       4.914035   -3.021227
constant                49.012173 -274.78631     282.399152 -164.033669

Weights W:
(This is the loading matrix)

                dailyCases_ts.l2      Rt_ts.l2 air_temp_ts.l2      constant
dailyCases_ts.d    -0.3925821122 -3.068507e-02  -4.581181e-03 -5.476077e-18
Rt_ts.d            -0.0002729301 -4.053662e-05   3.553009e-05 -3.788555e-21
air_temp_ts.d       0.0267354806 -7.791316e-03  -4.606410e-04  3.230168e-19

> summary(test2)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 2.649299e-01 1.139255e-01 6.869784e-02 1.110223e-16

Values of teststatistic and critical values of test:

           test 10pct  5pct  1pct
r <= 2 |  17.51  7.52  9.24 12.97
r <= 1 |  47.26 17.85 19.96 24.60
r = 0  | 122.98 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                    dailyCases_ts.l2     RH_ts.l2 apple_driving_ts.l2    constant
dailyCases_ts.l2           1.0000000   1.00000000            1.000000    1.000000
RH_ts.l2                  -8.9556211   0.18907898            6.123974    2.939054
apple_driving_ts.l2        0.3847621  -0.09244073            3.778865    1.394470
constant                 621.6903883 -12.39140162        -1103.827748 2208.110923

Weights W:
(This is the loading matrix)

                   dailyCases_ts.l2    RH_ts.l2 apple_driving_ts.l2      constant
dailyCases_ts.d         -0.03040052 -0.30292247        -0.006422801 -1.593734e-18
RH_ts.d                  0.05456596 -0.01887693        -0.002105843  3.767369e-19
apple_driving_ts.d      -0.09475738  0.24351208        -0.039664552 -1.121429e-17

> summary(test3)

###################### 
# Johansen-Procedure # 
###################### 

Test type: trace statistic , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 9.792497e-02 4.007579e-02 2.756594e-02 4.163336e-17

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  6.76  7.52  9.24 12.97
r <= 1 | 16.66 17.85 19.96 24.60
r = 0  | 41.60 32.00 34.91 41.07

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                         dailyCases_ts.l6 Google_workplace_ts.l6 Google_residential_ts.l6    constant
dailyCases_ts.l6                   1.0000               1.000000                 1.000000   1.0000000
Google_workplace_ts.l6          -118.3593               1.463141                -0.188060  -2.3164169
Google_residential_ts.l6        -317.5302              -5.856418                 1.804158  -0.6564643
constant                       -1110.0112              43.927921               -25.694469 313.4928351

Weights W:
(This is the loading matrix)

                        dailyCases_ts.l6 Google_workplace_ts.l6 Google_residential_ts.l6      constant
dailyCases_ts.d            -0.0001196841            -0.05311015              -0.12600019  1.187801e-18
Google_workplace_ts.d       0.0023961852            -0.03057509               0.01638121  6.280028e-19
Google_residential_ts.d     0.0003040770             0.0225


# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (34.91) < test value (72.91). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature.In the second hypothesis (r=1),value of 5 pct (19.96) < test value(23.92). Therefore there exist more than 2 co-integration relationship. Since in 3rd hypothesis, test value(4.76)< 5pct, existence of more than 3 co-integration relationship invalidated. Thus at most there are 2 co-integration relationship existed.
# Since in 3rd hypothesis, test value (17.51) > 5pct (9.24), there are more than 3 co-integration relationship existed between daily cases, Rh and apple driving.
# Since in 2nd hypothesis, test value (16.66) < 5pct (19.96), there are at most 1 co-integration relationship existed.




```{r}

# Johansen testing(MaxEigen)

print("------Eigen value testing----")

test1ei = ca.jo(system1, type='eigen', ecdet = 'const', K=K_val1)
test2ei = ca.jo(system2, type='eigen', ecdet = 'const', K=K_val2)
test3ei = ca.jo(system3, type='eigen', ecdet = 'const', K=K_val3)
test4ei = ca.jo(system4, type='eigen', ecdet = 'const', K=K_val4)
test5ei = ca.jo(system5, type='eigen', ecdet = 'const', K=K_val5)

summary(test1ei)
summary(test2ei)
summary(test3ei)
summary(test4ei)
summary(test5ei)

```

> summary(test1ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.805645e-01 7.491011e-02 1.917411e-02 5.531697e-18

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.76  7.52  9.24 12.97
r <= 1 | 19.15 13.75 15.67 20.20
r = 0  | 48.99 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                 dailyCases_ts.l2   Rt_ts.l2 air_temp_ts.l2    constant
dailyCases_ts.l2         1.000000    1.00000       1.000000    1.000000
Rt_ts.l2                 9.211152  -49.94739    -356.541761  828.080675
air_temp_ts.l2          -3.110456   13.14016       4.914035   -3.021227
constant                49.012173 -274.78631     282.399152 -164.033669

Weights W:
(This is the loading matrix)

                dailyCases_ts.l2      Rt_ts.l2 air_temp_ts.l2      constant
dailyCases_ts.d    -0.3925821122 -3.068507e-02  -4.581181e-03 -5.476077e-18
Rt_ts.d            -0.0002729301 -4.053662e-05   3.553009e-05 -3.788555e-21
air_temp_ts.d       0.0267354806 -7.791316e-03  -4.606410e-04  3.230168e-19

> summary(test2ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.477626e-01 2.708232e-02 1.822228e-02 2.316317e-19

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.45  7.52  9.24 12.97
r <= 1 |  6.64 13.75 15.67 20.20
r = 0  | 38.69 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                    dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6    constant
dailyCases_ts.l6           1.0000000   1.0000000            1.000000   1.0000000
RH_ts.l6                  -7.3608407   0.3965370            4.360072   0.4842979
apple_driving_ts.l6        0.2902885  -0.1255131            2.626363   1.0932876
constant                 511.1520401 -23.4892054         -793.423732 193.5741575

Weights W:
(This is the loading matrix)

                   dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6      constant
dailyCases_ts.d         -0.04837831 -0.14244464       -0.0052139939 -8.734074e-18
RH_ts.d                  0.06890610 -0.01469317       -0.0009433436  1.060041e-17
apple_driving_ts.d      -0.07231963  0.13641215       -0.0292459512 -1.060074e-17

> summary(test3ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 2.563121e-01 1.656282e-01 1.064700e-01 5.551115e-17

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 | 27.69  7.52  9.24 12.97
r <= 1 | 44.54 13.75 15.67 20.20
r = 0  | 72.85 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                         dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2    constant
dailyCases_ts.l2                1.0000000               1.000000                1.0000000    1.000000
Google_workplace_ts.l2         -0.4256884               3.446944               -0.5514188   -2.421722
Google_residential_ts.l2      -32.5242728               2.638470               -0.6803409   -1.856409
constant                      120.7067169              46.826178              -21.0843814 2177.286869

Weights W:
(This is the loading matrix)

                        dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2      constant
dailyCases_ts.d              0.011721881           -0.067451919              -0.26677034 -6.030348e-19
Google_workplace_ts.d       -0.008666682           -0.101053527               0.06610875  1.371053e-18
Google_residential_ts.d      0.018170612            0.005979858              -0.00418403 -4.553892e-20

> 

# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (22.00) < test value (48.99). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature. In the second hypothesis (r=1),value of 5 pct (15.67) < test value(19.15). Therefore there exist more that 2 co-integration relationship. Since in 3rd hypothesis, test value (4.76) < 5pct(9.24), existence of more than 3 co-integration relationship invalidated. Thus there exist at most 2 co-integration relationship.
# Only 1 co-integration relationship exist between daily cases, Rh and apple driving.
# There are more than 3 co-integration relationship exist between daily cases, goggle workplace and goggle residential.




>>>>>>> cbf417c0eaea52a33d3bbfc9a62d34415e26c31c:cointigration_2.Rmd
