---
title: "Cointegration_3"
author: "Syed Mohammed Tareq"
date: "3/11/2021"
output: html_document
---


```{r}


library(urca)
library(forecast)
library(tidyverse)
#install.packages("vars")
library(vars)
library(lmtest)

```




```{r}

# Loading the Dataset

data_frame = read_csv("https://raw.githubusercontent.com/QinLab/COVID19_transmission_MS/main/county3RWM/Ada%2C%20Idaho%2C%20US.csv?token=APMEIZBCR2ZB3H4USUJ4VFDAXEEEQ")

#data_frame <- read_csv("Accomack(Virginia).csv")
data_frame[is.na(data_frame)] = 0
data_frame

```





```{r}

# DailyCases were converted into time series data. Since dates were not mentioned in the  Date format (shown as string)
# Thus general index were used (1 to 248)
# Declaring time series object
dailyCases_ts = ts(data_frame$dailyCases, start = 1, end=248, frequency = 1)
air_temp_ts = ts(data_frame$air_temp, start = 1, end=248, frequency = 1)
RH_ts = ts(data_frame$RH, start = 1, end=248, frequency = 1)
Rt_ts = ts(data_frame$Rt, start = 1, end=248, frequency = 1)
apple_driving_ts = ts(data_frame$AppleDriving, start = 1, end=248, frequency = 1)
Google_workplace_ts = ts(data_frame$GoogleWorkplace, start = 1, end=248, frequency = 1)
Google_residential_ts = ts(data_frame$GoogleResidential, start = 1, end=248, frequency = 1)



```

# Bind into a system

```{r}
system1 = cbind(Rt_ts, air_temp_ts, RH_ts)
head(system1)

```


compare : 

Rt_ts : Reproduction No
apple_driving_ts : Apple driving
Google_workplace_ts: Google Mobility 


```{r}

system2 = cbind(Rt_ts, apple_driving_ts, Google_workplace_ts)
head(system2)

```

compare : 

Rt_ts : Reproduction No
Google_residential_ts : Google residential 
                
```{r}               
                
system3 = cbind(Rt_ts, Google_residential_ts)
head(system3)

```

#result for system1 

```{r}
# lag selection using VAR technique
lagselect1 = VARselect(system1, lag.max = 7, type = "const")
lagselect1


#lagselect1$selection

lagselect1$selection    
as.factor(lagselect1$selection)
summary(as.factor(lagselect1$selection))
sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])

K_val1 =strtoi(names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]))-1
K_val1



# suggestion value
if (K_val1<2){
  K_val1=2
  
}

K_val1


```

```{r}


# results for system2

lagselect2 = VARselect(system2, lag.max = 7, type = "const")
lagselect2

#lagselect2$selection
K_val2 =strtoi(names(sort(summary(as.factor(lagselect2$selection)), decreasing=T)[1]))-1

if (K_val2<2){
  K_val2=2
}
K_val2
```


# results for system3

```{r}


lagselect3 = VARselect(system3, lag.max = 7, type = "const")
lagselect3


#lagselect3$selection

K_val3 =strtoi(names(sort(summary(as.factor(lagselect3$selection)), decreasing=T)[1]))-1

if (K_val3<2){
  K_val3=2
}

K_val3

```

```{r}

# Johansen testing(trace)


# Test 1

test1 = ca.jo(system1, type='trace', ecdet = 'const', K=K_val1)
summary(test1)

```
# Discussion

# Null hypothesis (r = 0) is rejected as 5 pct value (34.91) < test value (75.85). Thus at least one co-integration relationship exist between Rt, air temperature and RH.

#In the second hypothesis (r=1),value of 5 pct (19.96) < test value(23.48). Therefore there exist more than 2 co-integration relationship. 

# Since in 3rd hypothesis (r=2), test value (4.86) < 5pct (9.24), there are at most 2 co-integration relationship existed.



```{r}


library(urca) 
library(vars) 
library(ggplot2)




# Cointegration equation 

w = Rt_ts - 0.1543125*air_temp_ts - 0.1029878*RH_ts + 6.2295908
plot(w, type="l")



```


```{r}

library("tseries")
adf.test(w)
 

```


```{r}



# Test 2

test2 = ca.jo(system2, type='trace', ecdet = 'const', K=K_val2)
summary(test2)


```
# Discussion

# Null hypothesis (r = 0) can not be rejected as 5 pct value (34.91) < test value (33.37). Thus is no co-integration relationship exist between Rt, Apple Driving Data and Google Workplace Data.

```{r}

# Cointegration equation 

w = Rt_ts - 0.00492720*apple_driving_ts + 0.01703786*Google_workplace_ts + 0.29134803
plot(w, type="l")


```


```{r}

library("tseries")
adf.test(w)

```


```{r}

# Test 3

test3 = ca.jo(system3, type='trace', ecdet = 'const', K=K_val3)
summary(test3)


```
# Discussion

# Null hypothesis (r = 0) is rejected as 5 pct value (19.96) < test value (20.79). Thus at least one co-integration relationship exist between Rt and Google Residential Data.

# Since in 2nd hypothesis (r =1), test value (7.73) < 5pct (9.24), there are at most 1 co-integration relationship existed.


```{r}
# Cointegration equation 

w = Rt_ts - 0.04911784*Google_residential_ts - 0.62663204
plot(w, type="l")


```

```{r}

library("tseries")
adf.test(w)




```

```{r}

# Johansen testing(MaxEigen)

print("------Eigen value testing----")

test1ei = ca.jo(system1, type='eigen', ecdet = 'const', K=K_val1)
test2ei = ca.jo(system2, type='eigen', ecdet = 'const', K=K_val2)
test3ei = ca.jo(system3, type='eigen', ecdet = 'const', K=K_val3)

summary(test1ei)
summary(test2ei)
summary(test3ei)


```

> summary(test1ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.805645e-01 7.491011e-02 1.917411e-02 5.531697e-18

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.76  7.52  9.24 12.97
r <= 1 | 19.15 13.75 15.67 20.20
r = 0  | 48.99 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                 dailyCases_ts.l2   Rt_ts.l2 air_temp_ts.l2    constant
dailyCases_ts.l2         1.000000    1.00000       1.000000    1.000000
Rt_ts.l2                 9.211152  -49.94739    -356.541761  828.080675
air_temp_ts.l2          -3.110456   13.14016       4.914035   -3.021227
constant                49.012173 -274.78631     282.399152 -164.033669

Weights W:
(This is the loading matrix)

                dailyCases_ts.l2      Rt_ts.l2 air_temp_ts.l2      constant
dailyCases_ts.d    -0.3925821122 -3.068507e-02  -4.581181e-03 -5.476077e-18
Rt_ts.d            -0.0002729301 -4.053662e-05   3.553009e-05 -3.788555e-21
air_temp_ts.d       0.0267354806 -7.791316e-03  -4.606410e-04  3.230168e-19

> summary(test2ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 1.477626e-01 2.708232e-02 1.822228e-02 2.316317e-19

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 |  4.45  7.52  9.24 12.97
r <= 1 |  6.64 13.75 15.67 20.20
r = 0  | 38.69 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                    dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6    constant
dailyCases_ts.l6           1.0000000   1.0000000            1.000000   1.0000000
RH_ts.l6                  -7.3608407   0.3965370            4.360072   0.4842979
apple_driving_ts.l6        0.2902885  -0.1255131            2.626363   1.0932876
constant                 511.1520401 -23.4892054         -793.423732 193.5741575

Weights W:
(This is the loading matrix)

                   dailyCases_ts.l6    RH_ts.l6 apple_driving_ts.l6      constant
dailyCases_ts.d         -0.04837831 -0.14244464       -0.0052139939 -8.734074e-18
RH_ts.d                  0.06890610 -0.01469317       -0.0009433436  1.060041e-17
apple_driving_ts.d      -0.07231963  0.13641215       -0.0292459512 -1.060074e-17

> summary(test3ei)

###################### 
# Johansen-Procedure # 
###################### 

Test type: maximal eigenvalue statistic (lambda max) , without linear trend and constant in cointegration 

Eigenvalues (lambda):
[1] 2.563121e-01 1.656282e-01 1.064700e-01 5.551115e-17

Values of teststatistic and critical values of test:

          test 10pct  5pct  1pct
r <= 2 | 27.69  7.52  9.24 12.97
r <= 1 | 44.54 13.75 15.67 20.20
r = 0  | 72.85 19.77 22.00 26.81

Eigenvectors, normalised to first column:
(These are the cointegration relations)

                         dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2    constant
dailyCases_ts.l2                1.0000000               1.000000                1.0000000    1.000000
Google_workplace_ts.l2         -0.4256884               3.446944               -0.5514188   -2.421722
Google_residential_ts.l2      -32.5242728               2.638470               -0.6803409   -1.856409
constant                      120.7067169              46.826178              -21.0843814 2177.286869

Weights W:
(This is the loading matrix)

                        dailyCases_ts.l2 Google_workplace_ts.l2 Google_residential_ts.l2      constant
dailyCases_ts.d              0.011721881           -0.067451919              -0.26677034 -6.030348e-19
Google_workplace_ts.d       -0.008666682           -0.101053527               0.06610875  1.371053e-18
Google_residential_ts.d      0.018170612            0.005979858              -0.00418403 -4.553892e-20

> 

# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (22.00) < test value (48.99). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature. In the second hypothesis (r=1),value of 5 pct (15.67) < test value(19.15). Therefore there exist more that 2 co-integration relationship. Since in 3rd hypothesis, test value (4.76) < 5pct(9.24), existence of more than 3 co-integration relationship invalidated. Thus there exist at most 2 co-integration relationship.
# Only 1 co-integration relationship exist between daily cases, Rh and apple driving.
# There are more than 3 co-integration relationship exist between daily cases, goggle workplace and goggle residential.





