---
title: "Cointegration_2"
author: "Syed Mohammed Tareq"
date: "2/26/2021"
output: html_document
---


```{r}


library(urca)
library(forecast)
library(tidyverse)
#install.packages("vars")
library(vars)
library(lmtest)

```




```{r}

# Loading the Dataset

data_frame = read_csv("https://raw.githubusercontent.com/QinLab/COVID19_transmission_MS/main/county3RWM/Adair%2C%20Missouri%2C%20US.csv?token=APMEIZCPMT7SO6QT26KMQ3DAWDNO4")

# data_frame <- read_csv("Data_Covid.csv")
data_frame[is.na(data_frame)] = 0
data_frame



```
```{r}

# DailyCases were converted into time series data. Since dates were not mentioned in the  Date format (shown as string)
# Thus general index were used (1 to 248)
# Declaring time series object
dailyCases_ts = ts(data_frame$dailyCases, start = 1, end=248, frequency = 1)
air_temp_ts = ts(data_frame$air_temp, start = 1, end=248, frequency = 1)
RH_ts = ts(data_frame$RH, start = 1, end=248, frequency = 1)
Rt_ts = ts(data_frame$Rt, start = 1, end=248, frequency = 1)
apple_driving_ts = ts(data_frame$AppleDriving, start = 1, end=248, frequency = 1)
Google_workplace_ts = ts(data_frame$GoogleWorkplace, start = 1, end=248, frequency = 1)
Google_residential_ts = ts(data_frame$GoogleResidential, start = 1, end=248, frequency = 1)



```


Lag values 


2 ~ 10    range of total lag Value
7 ~ 10    range of lag value  K=  1/4 OF DATE 




# Bind into a system


compare : 

Rt_ts : Reproduction No
air_temp_ts : air temperature 


```{r}
system1 = cbind(Rt_ts, air_temp_ts)
head(system1)

```


compare : 

Rt_ts : Reproduction No
air_temp_ts : Air temperature 

```{r}

system2 = cbind(Rt_ts, RH_ts)
head(system2)

```

compare : 

Rt_ts : Reproduction No
RH_ts : Relative humadity 
                
```{r}               
                
system3 = cbind(Rt_ts, apple_driving_ts)
head(system3)

```



```{r}
system4 = cbind(Rt_ts, Google_workplace_ts)
head(system4)

```

```{r}

system5 = cbind(Rt_ts, Google_residential_ts)
head(system5)

```

```{r}
# lag selection using VAR technique
lagselect1 = VARselect(system1, lag.max = 7, type = "const")
lagselect1


#lagselect1$selection

lagselect1$selection #   
as.factor(lagselect1$selection)
summary(as.factor(lagselect1$selection))
sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])

K_val1 =strtoi(names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]))-1
K_val1



# According to Johansen criteria
if (K_val1<2){
  K_val1=2
  
}


```

AIC : 
# results for system2








```{r}

# lag = 7

# time-point 100 days    before 100 days  then forecast  next 100 day data 

lagselect2 = VARselect(system2, lag.max = 7, type = "const")
#lagselect2$selection
K_val2 =strtoi(names(sort(summary(as.factor(lagselect2$selection)), decreasing=T)[1]))-1

if (K_val2<2){
  K_val2=2
}
K_val2
```


# results for system3

```{r}


lagselect3 = VARselect(system3, lag.max = 7, type = "const")
#lagselect3$selection
K_val3 =strtoi(names(sort(summary(as.factor(lagselect3$selection)), decreasing=T)[1]))-1

if (K_val3<2){
  K_val3=2
}

K_val3

```
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
$criteria
              1        2        3        4        5        6        7
AIC(n) 1.128403 1.095402 1.104286 1.110670 1.139414 1.177879 1.172366
HQ(n)  1.198310 1.217739 1.279053 1.337866 1.419041 1.509936 1.556853
SC(n)  1.301920 1.399057 1.538079 1.674599 1.833481 2.002085 2.126709
FPE(n) 3.090744 2.990532 3.017503 3.037346 3.126771 3.250677 3.234567

> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 

> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     7      7      1      7      
Levels: 1 7
> lagselect1$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2 
> as.factor(lagselect1$selection)
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      1      1      2
> sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1]
1 
2 
> names(sort(summary(as.factor(lagselect1$selection)), decreasing=T)[1])
[1] "1"


    
```{r}

lagselect4 = VARselect(system4, lag.max = 7, type = "const")
#lagselect3$selection
K_val4 =strtoi(names(sort(summary(as.factor(lagselect4$selection)), decreasing=T)[1]))-1

if (K_val4<2){
  K_val4=2
}

K_val4

```


```{r}

lagselect5 = VARselect(system5, lag.max = 7, type = "const")
#lagselect3$selection
K_val5 =strtoi(names(sort(summary(as.factor(lagselect5$selection)), decreasing=T)[1]))-1

if (K_val5<2){
  K_val5=2
}

K_val5

```


```{r}


# Johansen testing(trace)


# Test 1

test1 = ca.jo(system1, type='trace', ecdet = 'const', K=K_val1)
print(summary(test1))


```
```{r}


library(urca) 
library(vars) 
library(ggplot2)



# Cointegration equation 

w = Rt_ts - 0.09512352*air_temp_ts + 0.52451221
plot(w, type="l")

```




```{r}

library("tseries")
adf.test(w)



```


```{r}
# Test 2

test2 = ca.jo(system2, type='trace', ecdet = 'const', K=K_val2)
summary(test2)


```

```{r}


# Cointegration equation 

w = Rt_ts - 0.585244*RH_ts + 40.752619
plot(w, type="l")





```

```{r}


library("tseries")
adf.test(w)


```


```{r}
# Test 3

test3 = ca.jo(system3, type='trace', ecdet = 'const', K=K_val3)
summary(test3)

```




```{r}

# Cointegration equation 

w = Rt_ts - 0.008621693*apple_driving_ts + 0.263179855
plot(w, type="l")



```



```{r}

library("tseries")
adf.test(w)

```



```{r}


# Test 4

test4 = ca.jo(system4, type='trace', ecdet = 'const', K=K_val4)
summary(test4)


```




```{r}

# Cointegration equation 

w = Rt_ts + 0.03684679*Google_workplace_ts - 0.09311791
plot(w, type="l")



```



```{r}

library("tseries")
adf.test(w)


```


```{r}

# Test 5 

test5 = ca.jo(system5, type='trace', ecdet = 'const', K=K_val5)
summary(test5)


```

```{r}

# Cointegration equation 

w = Rt_ts + 0.9075647*Google_residential_ts - 1.3227187
plot(w, type="l")



```




```{r}

library("tseries")
adf.test(w)



```




```{r}


# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (34.91) < test value (72.91). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature.In the second hypothesis (r=1),value of 5 pct (19.96) < test value(23.92). Therefore there exist more than 2 co-integration relationship. Since in 3rd hypothesis, test value(4.76)< 5pct, existence of more than 3 co-integration relationship invalidated. Thus at most there are 2 co-integration relationship existed.
# Since in 3rd hypothesis, test value (17.51) > 5pct (9.24), there are more than 3 co-integration relationship existed between daily cases, Rh and apple driving.
# Since in 2nd hypothesis, test value (16.66) < 5pct (19.96), there are at most 1 co-integration relationship existed.


```

```{r}

# Johansen testing(MaxEigen)

print("------Eigen value testing----")

test1ei = ca.jo(system1, type='eigen', ecdet = 'const', K=K_val1)
summary(test1ei)


```

```{r}

# Cointegration equation 

w = Rt_ts - .09512352*air_temp_ts + 0.52451221
plot(w, type="l")



```


```{r}

library("tseries")
adf.test(w)



```




```{r}



test2ei = ca.jo(system2, type='eigen', ecdet = 'const', K=K_val2)
summary(test2ei)

```



```{r}

# Cointegration equation 

w = Rt_ts - 0.585244*RH_ts + 40.752619
plot(w, type="l")


```



```{r}

library("tseries")
adf.test(w)


```


```{r}


test3ei = ca.jo(system3, type='eigen', ecdet = 'const', K=K_val3)
summary(test3ei)


```



```{r}

# Cointegration equation 

w = Rt_ts - 0.008621693*apple_driving_ts + 0.263179855
plot(w, type="l")


```




```{r}

library("tseries")
adf.test(w)


```



```{r}


test4ei = ca.jo(system4, type='eigen', ecdet = 'const', K=K_val4)
summary(test4ei)



```




```{r}

# Cointegration equation 

w = Rt_ts + 0.03684679*Google_workplace_ts - 0.09311791
plot(w, type="l")


```

```{r}

library("tseries")
adf.test(w)



```





```{r}


test5ei = ca.jo(system5, type='eigen', ecdet = 'const', K=K_val5)
summary(test5ei)



```




```{r}

# Cointegration equation 

w = Rt_ts + 0.9075647*Google_residential_ts - 1.3227187
plot(w, type="l")


```




```{r}

library("tseries")
adf.test(w)


```


```{r}

> summary(test1ei)

# Discussion
# Null hypothesis (r = 0) is rejected as 5 pct value (22.00) < test value (48.99). Thus at least one co-integration relationship exist between daily cases, Rt and air temperature. In the second hypothesis (r=1),value of 5 pct (15.67) < test value(19.15). Therefore there exist more that 2 co-integration relationship. Since in 3rd hypothesis, test value (4.76) < 5pct(9.24), existence of more than 3 co-integration relationship invalidated. Thus there exist at most 2 co-integration relationship.
# Only 1 co-integration relationship exist between daily cases, Rh and apple driving.
# There are more than 3 co-integration relationship exist between daily cases, goggle workplace and goggle residential.




